Source Summaries

### 2020-04-26 paper/sourceSummaries/summary10.tex
Last source summary :tear:

@@

@@

@@

@@

@@

@@

>>>>

\noindent
\subsection{Designing and implementing malicious hardeware}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{kignDesigning08}

@@

\noindent
The authors propose that attackers can design and attack malicious hardware to carry out attacks rather than attack the software.  They also propose that this attack vector is harder to detect and would bypass security implemented at the software level.

@@

\noindent
Game Theory.  The authors propose and attempt an attack vector that would bypass the security of a system entirely.

@@

\noindent
The authors designed two different "Illinois Malicious Processors" to be placed on the victim hardware and they created three attacks to implement with this hardware.  The IMPs were made using modified Leon3 processors.  The first design attacked the memory of the victim hardware and their second was a complete hardware shim between the victim hardware and the victim software. They then developed a Privilege Escalation attack, a login backdoor, and a password stealer.

@@

\noindent
The authors found that their attacks added less than 0.1 percent more logic gates to the base system and they propose that this would be even less on a larger, more complicated victim.  They also found that compared to the normal operations of the system a one time attack only increased the operation time by 1.34\% and a persistent attack only increased the operation time by 13.0\%.

@@

\noindent
The authors do not propose any specific future work, however, it would be beneficial to continue to develop hardware that would not be detected via current means of supply chain attack detection.  Most notably analog power analysis, chip identification, and operation timing detection.
